Online Supporting Information

### 2020-11-30 documents/ovando-et-al-pop-effects-of-mpas-si.Rmd
updating SI

```{r, include=FALSE}
library(sf)
library(ggmap)
library(viridis)
library(hrbrthemes)
library(scales)
library(patchwork)
library(rpart)
library(extrafont)
library(caret)
library(ggsci)
library(rEDM)
library(tidyverse)
library(ggtext)
library(rstan)
library(rstanarm)
library(bayesplot)
library(Synth)
library(here)

@@

>>>>

```{r, include=FALSE}
library(sf)
library(ggmap)
library(viridis)
library(hrbrthemes)
library(scales)
library(patchwork)
library(rpart)
library(extrafont)
library(caret)
library(ggsci)
library(rEDM)
library(tidyverse)
library(ggtext)
library(rstan)
library(rstanarm)
library(bayesplot)
library(Synth)
library(here)
library(modelsummary)
library(sandwich)

@@

We also ran a frequentist version of our results, as further demonstration that our results are not driven by our priors or Bayesian framework in general. For this version we applied a Newey-West correction to the standard errors to account for the clustering of the observations in space and time (Fig.\@ref(fig:freq-did)).

```{r freq-did, fig.cap="Frequentist version of core difference-in-difference model, with standard errors adjusted by Newey-West correction to reflect clustering in space and time. Points are mean estimate, error bars 95% confidence interval."}

did_dat  <- model_runs$did_fit[[which(model_runs$data_source == "pisco" & model_runs$var_names == "pisco_a" & model_runs$data_to_use == "all")]]$did_data

did_reg <-
  lm(
    log(total_biomass_density) ~ targeted * year_bins + site_side - 1 + var_tex + var_tex_2
    + var_surge + var_kelp + var_lag_catch + var_temp +
      regional_temp_dev + regional_temp_dev_2,
    weights = did_data$weight,
    data = did_data
  )

a = vcovPL(did_reg, cluster = ~  region +year,lag = "NW1994")

freq_did <- broom.mixed::tidy(did_reg) %>% 
  mutate(se = sqrt(diag(a))) %>% 
  mutate(effect = exp(estimate + se^2 / 2) - 1)

freq_did %>% 
  filter(str_detect(term, "targeted:")) %>% 
  mutate(term = str_remove_all(term, "targeted:year_bins")) %>% 
  ggplot(aes(term, estimate)) + 
  geom_hline(aes(yintercept = 0)) +
  geom_pointrange(aes(ymin = estimate - 1.96 * se, ymax = estimate + 1.96 * se)) + 
    scale_y_continuous(name = "MPA Effect") +
  scale_x_discrete(name = element_blank())
